---
title: "Data Science - Assignment"
author: "Amrutha E"
date: "25/03/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Que 1
Complete the following Generic ANOVA table:
## Que 2
What     is the difference between a linear model using glm( ) and a linear model using lm( ) in R?

### ans

#### glm()
glm() is used to fit generalized linear models, specified by giving a symbolic description of the linear predictor and a description of the error distribution.

#### lm()
In R, the lm(), or “linear model,” function can be used to create a simple regression model.  


In R, using lm() is a special case of glm().
lm() fits models following the form Y = Xb + e, where e is Normal (0 , s^2^).
glm() fits models following the form f(Y) = Xb + e. However, in glm both the function f(Y) (the 'link function') and the distribution of the error term e can be specified. Hence the name - 'generalised linear model'.
If you are getting the same results using both lm() and glm(), it is because for glm(), f(Y) defaults to Y, and e defaults to Normal (0, s^2^). i.e. if you don't specify the link function and error distribution, the parameters that glm() uses produce the same effect as running lm().

## Que 3
Solve the following Probability distribution problems using R:

1. Suppose widgit weights produced at Acme Widgit Works have weights that are normally distributed with mean 17.46 grams and variance 375.67 grams. What is the probability that a randomly chosen widgit weighs more than 19 grams?

### ans
**Question Rephrased** : What is P(X > 19) when X has the N(17.46, 375.67) distribution? 
pnorm() is the R function that calculates the Cumulative distribution function
R wants the s. d. as the parameter, not the variance. We'll need to take a square root! 
```{r}
1 - pnorm(19, mean=17.46, sd=sqrt(375.67))
```


2. Suppose IQ scores are normally distributed with mean 100 and standard deviation 15. What is the 95th percentile of the distribution of IQ scores

### ans
**Question Rephrased** : What is F^-1^(0.95) when X has the N(100, 152) distribution? 
The qnorm function is simply the inverse of the Cumulative distribution function
```{r}
qnorm(0.95, mean = 100, sd = 15)
```

## Que 4
With     the help of suitable examples explain attach and detach     functions in R for data frames and packages

### ans
The attach function allows to access variables of a data frame without calling the data frame.
Create an example data frame
```{r}
data <- data.frame(x1 = c(9, 8, 3, 4, 8),         
                   x2 = c(5, 4, 7, 1, 1),
                   x3 = c(1, 2, 3, 4, 5))
data                                              
```
Let’s assume that we want to work with the first column X1. If we try to call the column with the following code, R returns an error message:
```{r}
# x1
# Error: object 'x1' not found
```
However, if we attach the data frame first…
```{r}
attach(data) 
x1  
# 9 8 3 4 8
```
After finishing the work on our data frame, it is advisable to detach the data. Otherwise, the R code might get difficult to use afterwards.
We can detach our data with the following line of code:
```{r}
detach(data)
```
After detaching, we cannot work with the X1 column as before anymore:
```{r}
# x1 
# Error: object 'x1' not found
```

# Que 5
We have a sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as   
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld", "vic", 
           "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa", "vic", 
           "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
```
We have the incomes of the same tax accountants in another vector (in suitably large units of money)
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 
             70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 
             49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```
### ans
A factor is created using the factor() function
```{r}
state_factor <- factor(state)
print(state_factor)
```
To  calculate  the  sample  mean  income  for  each  state  we  can  now  use  the  special function tapply()
```{r}
income_means <- tapply(incomes, state_factor, mean)
print(income_means)
```


## Que 6
Write short notes on cbind and rbind using suitable examples

### ans

#### rbind()
The name of the rbind R function stands for row-bind. The rbind function can be used to combine several vectors, matrices and/or data frames by rows.
The easiest way of using rbind in R is the combination of a vector and a data frame
```{r}
x1 <- c(7, 4, 4, 9)                  # Column 1 of data frame
x2 <- c(5, 2, 8, 9)                  # Column 2 of data frame
x3 <- c(1, 2, 3, 4)                  # Column 3 of data frame
data_1 <- data.frame(x1, x2, x3)     # Create example data frame
print(data_1)
```
and an example vector:
```{r}
vector_1 <- c(9, 8, 7)               # Create example vector
```
Now, let’s rbind this vector to the data frame:
```{r}
rbind(data_1, vector_1)              # rbind vector to data frame
print(data_1)
```

#### cbind()
The name of the cbind R function stands for column-bind. The cbind function is used to combine vectors, matrices and/or data frames by columns.
A popular way of using the cbind command in the R programming language is the combination of a vector and a data.frame. 
```{r}
data_1 <- data.frame(x1 = c(7, 3, 2, 9, 0),          # Column 1 of data frame
                     x2 = c(4, 4, 1, 1, 8),          # Column 2 of data frame
                     x3 = c(5, 3, 9, 2, 4))          # Column 3 of data frame
```
and an example vector / column:
```{r}
y1 <- c(9, 8, 7, 6, 5)                               # Create vector
```
Now, we can cbind this vector as new column to our example data frame:
```{r}
data_new1 <- cbind(data_1, y1)                       # cbind vector to data frame
data_new1                                            # Print data to RStudio console
```

