---
title: "Data Science - Assignment"
author: "Amrutha E"
date: "25/03/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Que 1

## Que 2

## Que 3

## Que 4

## Que 5
We have a sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as   
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld", "vic", 
           "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa", "vic", 
           "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
```
We have the incomes of the same tax accountants in another vector (in suitably large units of money)
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 
             70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 
             49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```
### ans
A factor is created using the factor() function
```{r}
state_factor <- factor(state)
print(state_factor)
```
To  calculate  the  sample  mean  income  for  each  state  we  can  now  use  the  special function tapply()
```{r}
income_means <- tapply(incomes, state_factor, mean)
print(income_means)
```


## Que 6
Write short notes on cbind and rbind using suitable examples

### ans

#### rbind()
The name of the rbind R function stands for row-bind. The rbind function can be used to combine several vectors, matrices and/or data frames by rows.
The easiest way of using rbind in R is the combination of a vector and a data frame
```{r}
x1 <- c(7, 4, 4, 9)                  # Column 1 of data frame
x2 <- c(5, 2, 8, 9)                  # Column 2 of data frame
x3 <- c(1, 2, 3, 4)                  # Column 3 of data frame
data_1 <- data.frame(x1, x2, x3)     # Create example data frame
print(data_1)
```
and an example vector:
```{r}
vector_1 <- c(9, 8, 7)               # Create example vector
```
Now, let’s rbind this vector to the data frame:
```{r}
rbind(data_1, vector_1)              # rbind vector to data frame
print(data_1)
```

#### cbind()
The name of the cbind R function stands for column-bind. The cbind function is used to combine vectors, matrices and/or data frames by columns.
A popular way of using the cbind command in the R programming language is the combination of a vector and a data.frame. 
```{r}
data_1 <- data.frame(x1 = c(7, 3, 2, 9, 0),          # Column 1 of data frame
                     x2 = c(4, 4, 1, 1, 8),          # Column 2 of data frame
                     x3 = c(5, 3, 9, 2, 4))          # Column 3 of data frame
```
and an example vector / column:
```{r}
y1 <- c(9, 8, 7, 6, 5)                               # Create vector
```
Now, we can cbind this vector as new column to our example data frame:
```{r}
data_new1 <- cbind(data_1, y1)                       # cbind vector to data frame
data_new1                                            # Print data to RStudio console
```

