---
title: "Data Science - Assignment"
author: "Amrutha E"
date: "25/03/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Que 1

## Que 2

## Que 3

## Que 4

## Que 5
We have a sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as   
```{r}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld", "vic", 
           "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt", "wa", "vic", 
           "qld", "nsw", "nsw", "wa", "sa", "act", "nsw", "vic", "vic", "act")
```
We have the incomes of the same tax accountants in another vector (in suitably large units of money)
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54, 62, 69, 
             70, 42, 56, 61, 61, 61, 58, 51, 48, 65, 
             49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```
### ans
A factor is created using the factor() function
```{r}
state_factor <- factor(state)
print(state_factor)
```
To  calculate  the  sample  mean  income  for  each  state  we  can  now  use  the  special function tapply()
```{r}
income_means <- tapply(incomes, state_factor, mean)
print(income_means)
```


## Que 6
